Implications of afforestation policies for global markets

### 2024-02-25 paper.Rmd
Update paper.Rmd

>>>>

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any positive price impacts resulting from this policy, with the price of agricultural goods decreasing 0.2 percent (table 5). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.1 and 2.8 percent.

Table 5
									∆ (%)				
	Agricultural Goods		Forest Products		Lumber		Paper Products		Other Non-Agricultural Goods
Oceania					0.6	0.3	0.3	0.3	0.3
China					0.7	0.3	0.2	0.2	0.3
Japan					-0.2	0.2	0.2	0.2	0.2
East Asia				2.8	0.2	0.2	0.2	0.2
Southeast Asia				1.5	0.2	0.2	0.2	0.2
South Asia				1.6	0.2	0.2	0.1	0.2
Canada					0.4	0.3	0.3	0.3	0.4
United States				0.4	0.3	0.3	0.3	0.3
Central America				1.3	0.2	0.2	0.2	0.2
Brazil					0.7	0.3	0.3	0.3	0.3
Rest of South America			1.1	0.2	0.2	0.2	0.2
European Union				0.5	0.2	0.2	0.2	0.2
EUII					0.6	0.3	0.2	0.2	0.2
Russia					0.6	0.2	0.2	0.2	0.2
Sub-Saharan Africa			0.9	0.3	0.2	0.2	0.3
North Africa & the Middle East		1.1	0.2	0.2	0.2	0.2
